The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-03-12 manuscript/manuscript.tex
Re-sort the section with John's suggestion

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references. Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent. Thus, we adopt the virial formalism from \citet{Schulze2018}:
\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}

@@

@@

\begin{deluxetable}{llccc}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Sample properties.} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243\\
COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600\\ 
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
}
\end{deluxetable}

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Inferred \mbh\ .} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
}
\end{deluxetable*}

>>>>

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references. Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent. Thus, we adopt the virial formalism from \citet{Schulze2018}:

@@

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}

@@

\begin{deluxetable}{llcccc}
\tablecolumns{6}
\tablewidth{0pt}
\tablecaption{Sample properties.} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 \\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 \\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 \\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 \\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\ 
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 \\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 \\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 \\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 \\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
}
\end{deluxetable}

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Inferred \mbh\ .} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
CDFS-1 & 5449.4022 & 43.08 & 8.789 & ... & ... & ... \\
CDFS-229 & 2254.0105 & 43.3 & 8.082 & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
CDFS-724 & 3342.3888 & 42.81 & 8.21 & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
}
\end{deluxetable*}
